---
title: "Introduction to SA23204185"
author: "SA23204185"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to SA23204185}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__SA23204185__  package is a simple R package that implements the _IPW_ algorithm and the _distribute_ algorithm described in the paper. It is capable of recovering a missing matrix in a distributed setting along with its corresponding right singular vectors. For convenience, we have directly encapsulated the simulation process in _distribute_monte_, so that by simply inputting the parameters, you can obtain the recovery discrepancy of the right singular vectors.This package also contains a cpp function _DAP_  calculate the  probability of  a certain number 'target' out of n (target <= n) delivery man with respectively different probability to accept an order.



## R function

#### IPW algorithm

```{r}
IPW <- function(M, K) {
    n <- nrow(M)
    d <- ncol(M)
    Y <- ifelse(M == 0, 0, 1) 
    
    p_hat <- sum(Y) / (n * d)
    
    Sigma_phat <- crossprod(M) - (1 - p_hat) * diag(colSums(M^2))
    
    eigen_Sigma_phat <- eigen(Sigma_phat)
    
    V <- eigen_Sigma_phat$vectors[, 1:K]
    
    return(V = V)
}
```

* Clearly, the above code can handle individual missing matrices and return their right singular vectors.


#### distribute algorithm
```{r}
distribute <- function(matrices_get) {
    n <- nrow(matrices_get[[1]])
    d <- ncol(matrices_get[[1]])
    m <- length(matrices_get)
    
    Sigma_tilde <- matrix(0, d, d)
    V <- vector("list", m)
    
    for (i in 1:m) {
        V[[i]] <- IPW(matrices_get[[i]])
        Sigma_tilde <- Sigma_tilde + (1 / m) * V[[i]] %*% t(V[[i]])
    }
    
    V_res <- eigen(Sigma_tilde)$vec[, 1:2]
    return(V_res)
}
```

* Clearly, it is evident that the above code can handle matrix columns and utilize the method described in the paper to return more accurate estimates of the right singular vectors.

* Both of the above algorithms are preparing for numerical simulations in the paper.

## A Cpp function 

  This package also contains a cpp function to calculate the  probability of  a certain number 'target' out of n (target <= n) delivery man with respectively different probability to accept an order.
  In this case you input a  vector which contain probability of whether these delivery men will accept current order or not,the objective number of delivery men accepting the order and the total number of delivery men.The R code to call this function is as follows

```{r}
library(Rcpp)
cppFunction(code='double  targetoutofn(NumericVector x, int target, int n) {
    double prob[n+1][target+1];
    prob[0][0] = 1;
    for(int i = 1; i <= n; i++){
        prob[i][0] = prob[i-1][0]*(1-x[i-1]);
    }
    for(int i = 1; i <= n; i++){
        for(int k = 1; k <= i && k <= target; k++){
            prob[i][k] = prob[i-1][k] * (1-x[i-1]) + prob[i-1][k-1] * x[i-1];
        }
    }
    return prob[n][target];
    }')
prob <- c(0.5, 0.5, 0.5, 0.5, 0.5)
target <- 1
n <- 5
targetoutofn(prob, target, n)
```

