---
title: "Introduction to SA23204185"
author: "SA23204185"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to SA23204185}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__SA23204185__  package is a simple R package that implements the _IPW_ algorithm and the _Distributed_ algorithm described in the paper. It is capable of recovering a missing matrix in a distributed setting along with its corresponding right singular vectors.This package also contains a cpp function _targetoutofn_   calculate the  probability of  a certain number 'target' out of n (target <= n) delivery man with respectively different probability to accept an order.



## CrossValidation  _add_

```{r}
add <- function(a,b){
    return(a+b)
}

```

## A Cpp function 

  This package also contains a cpp function to calculate the  probability of  a certain number 'target' out of n (target <= n) delivery man with respectively different probability to accept an order.
  In this case you input a  vector which contain probability of whether these delivery men will accept current order or not,the objective number of delivery men accepting the order and the total number of delivery men.The R code to call this function is as follows

```{r}
library(Rcpp)
cppFunction(code='double  targetoutofn(NumericVector x, int target, int n) {
    double prob[n+1][target+1];
    prob[0][0] = 1;
    for(int i = 1; i <= n; i++){
        prob[i][0] = prob[i-1][0]*(1-x[i-1]);
    }
    for(int i = 1; i <= n; i++){
        for(int k = 1; k <= i && k <= target; k++){
            prob[i][k] = prob[i-1][k] * (1-x[i-1]) + prob[i-1][k-1] * x[i-1];
        }
    }
    return prob[n][target];
    }')
prob <- c(0.5, 0.5, 0.5, 0.5, 0.5)
target <- 1
n <- 5
targetoutofn(prob, target, n)
```

